### 2012-03-20 doc/theses/mikula/combination_with_existing_methods_of_inference.tex
Master thesis: In progress.

\chapter{Combination with Existing Methods of Inference}
In this chapter, we describe how to incorporate the inferred statements with existing methods of XML schema inference. We focus on a class of methods which are based on a creation and subsequent simplification of the initial grammar (as discussed in Chapter \ref{chapter_analysis_of_recent_approaches}).

@@

The selection of elements is a simplified XPath evaluation. The simplification involves the aspects; the evaluation is not performed upon XML data, but the simplified grammar containing rules with a regular expression on their right side, and, partially related, predicates in path steps are not evaluated, they are ignored.

@@

%In the case of inferred types, the situation is not that simple, because there can occur conflicting statements. In %particular, two kinds of conflicts can emerge between two statements.
%
%\begin{enumerate}
%\item The two types do not equal, but one is castable to the other.
%\item The two types do not equal and none of them is castable to the other.
%\end{enumerate}
%
%The example of conflict of the first kind for path $p$ without predicates is $p_1 \rightarrow date$, $p_2 \rightarrow %string$. And another one is $p_1 \rightarrow byte$, $p_2 \rightarrow int$, where $p_1$, $p_2$ are paths that when %stripped of predicates, they equal $p$. There are two reasons of this kind of conflicts.
%
%The first reason is that both types are inferred correctly for nodes targeted by $p$, but one of them was inferred from a %more convenient expression and is more precise. Consider these two expressions; $PathType$ $p$ is compared to an integer %literal constant, and, $PathType$ $p$ is an argument of function where a formal type of the argument is byte. The first %expression is utilized to infer statement $p \rightarrow integer$, and the second one to infer statement $p \rightarrow %byte$. Both of the types are correct, but the second one is more accurate.

From all inferred types for a particular path, the most specific (the most accurate) is selected and assigned to respective nodes from the grammar targeted by the path.

>>>>

\chapter{Combination with Existing Methods of Inference} \label{CHAPTER_combination_with_existings_methods_of_inference}
In this chapter, we describe how to incorporate the inferred statements to existing methods of XML schema inference. We focus on a class of methods which are based on a creation and subsequent simplification of the initial grammar (as discussed in Chapter \ref{chapter_analysis_of_recent_approaches}).

@@

The selection of elements is a simplified XPath evaluation. The simplification involves two aspects; the evaluation is not performed upon XML data, but the simplified grammar containing rules with a regular expression on their right side, and, partially related, predicates in path steps are not evaluated, they are ignored.

@@

A problem emerges for example if PathType $p$ is compared to an integer constant, and the real type of elements (or attributes) selected by $p$ is \texttt{double}. In that case, statement $p \rightarrow$ \texttt{integer} is inferred, but it is not correct.

\subsection{Verification using XML data}
To solves those problems, we propose a simple verification using XML data.

For each PathType $p$ that occurs in the inferred type statements $\mathcal{S}_t$, we find set $T_p$ of all inferred types. $T_p = \{t|(p \rightarrow t) \in \mathcal{S}_t\}$. Then, we create sequence $T_p'$ by ordering the set $T_p$ from the most specific type to the most general one. For example, if $T_p = \{$\texttt{double}, \texttt{byte}, \texttt{int}$\}$, $T_p' = ($\texttt{byte}, \texttt{int}, \texttt{double}$)$.

Since we have the XML data and path $p$ is XQuery path, we can use an XQuery process (a program that evaluates XQuery paths or queries) to select nodes $N$ targeted by $p$. The verification algorithms iterates through $T_p'$ and for each $t' \in T_p'$ it checks if every node in $N$ conforms to $t'$. If so, $t'$ is the inferred type for nodes $N$ (and PathType $p$), else the inferred type is \texttt{string}.
